Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-23 PAPER.tex
added additional ref to Appendix

{\bf In general:} Another way to phrase the shortcoming of the inverse covariance estimator is that it is not properly normalized. Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data. However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data. The power spectrum estimate will therefore be incorrectly normalized, which manifests as signal loss. We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics.

>>>>

{\bf In general:} Another way to phrase the shortcoming of the inverse covariance estimator (which is also discussed in Appendix \ref{sec:sigloss_appendix}) is that it is not properly normalized. Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data. However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data. The power spectrum estimate will therefore be incorrectly normalized, which manifests as signal loss. We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics.
